Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-04-26 paper/ms.tex
Update figures in paper
Makes them all standardized

\begin{figure*}[h!]%
\centering
\includegraphics[width=0.8\textwidth]{fig/fig1.pdf}
\caption{Surface density projections in an \Nbody{} only simulation (upper
panels) and a simulation which includes the SMUGGLE model (bottom panels). We
can see that in the \Nbody{} run, the bar grows in length and strength. In the
SMUGGLE run (which includes a gaseous phase and a model for the multi-phase
interstellar medium), the bar remains at approximately the same length and
strength over the course of the simulation. The \Nbody{} model is identical to
the GALAKOS model, discussed in the text.}\label{fig:overview}
\end{figure*}

\begin{figure}[h!]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig2.pdf}
\caption{Various bar properties from the \Nbody{} and SMUGGLE runs. The
\textit{upper panel} show the evolution of the pattern speed. As expected, the
bar in the \Nbody{} run slows down due to interactions between the bar and the
dark matter halo. However, the bar in the SMUGGLE run does not slow down and
instead remains at a constant pattern speed. The \textit{middle panel} shows
the evolution of the bar length. In the \Nbody{} case, the bar lengthens. This
occurs because as the pattern speed drops, bar-like orbits at larger radii are
possible. Stars are captured on these orbits, lengthening the bar. This
process does not occur in the SMUGGLE cases since the bar pattern speed is not
decreasing, and therefore the bar length remains constant. The \textit{lower
panel} shows the torque on the bar by different components. The solid lines
show the torque exerted by the halo in both the \Nbody{} and SMUGGLE cases. The
dashed line shows the torque exerted by the gas phase in the SMUGGLE run
(there is no gas in the \Nbody{} run). Details on how these properties
are calculated is given in the Methods section.}\label{fig:prop}
\end{figure}

\begin{figure*}[h!]%
\centering
\includegraphics[width=0.9\textwidth]{fig/fig3.pdf}
\caption{The wake excited in the dark matter halo in the \Nbody{} case
(\textit{left panel}) and SMUGGLE case (\textit{right panel}) after
$2.6\,\textrm{Gyr}$. The \textit{left} and \textit{right panels} show a
surface density projection in the $x$-$y$ plane of the dark matter halo after
an axisymmetric average has been subracted. The solid line indicates the
direction of the bar while the dashed line indicates the direction of the halo
wake (both measured by taking the second Fourier component within a sphere of
all material within a radius of $X\,\textrm{kpc}$). The \textit{center panel}
shows the time evolution of the angle difference between the bar and the halo
wake, as measured from the second Fourier component. After the first Gyr, the
angle difference in the SMUGGLE case is smaller than in the \Nbody{} case by
about a factor of two, reflecting how the dark matter halo in the SMUGGLE case
is unable to exert as negative a torque on the bar as in the \Nbody{}
case.}\label{fig:wake}
\end{figure*}

\begin{figure}[h!]
\centering
\includegraphics{fig/fig4.pdf}
\caption{The torque on the bar by the gas when the pattern speed of the bar is
kept at a constant value. Only gas within the corotation radius is able to
infall. Since slower bars have larger corotation radii, slower bars experience
a larger net torque than faster bars. The setup of the simulations used here
is identical to the SMUGGLE case discussed earlier and in the Methods section,
except the \Nbody{} disk is rotated as a solid body with a constant angular
velocity.}\label{fig:equil}
\end{figure}

@@

\begin{figure}[t]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-vcirc.pdf}
\caption{The circular velocity curve for the \Nbody{} run (blue) and the SMUGGLE
run (orange) compared to observational estimates.\cite{2019ApJ...871..120E} We
see that the circular velocity curve for both runs is marginally larger than
the Milky Way's, but still comparable. The SMUGGLE circular velocity curve is
larger than the \Nbody{} curve due to the additional mass in the gas phase.}
\label{fig:vcirc}
\end{figure}

@@

\begin{figure}[t!]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-surf.pdf}
\caption{The time evolution of the gas surface density (\textit{upper}) and
the star formation rate (SFR) surface density (\textit{lower}) at various
times during the simulation. Colored lines indicate the profiles at selected
times during the simulation while the horizontal dashed lines indicate
approximate values for the Milky Way.\cite{2012ARAA..50..531K} We see that the
gas surface density is slightly higher but within an order of magnitude of the
Milky Way's typical gas surface density. We see a sharp decrease in the gas
and SFR surface density along the extent of the bar from $\sim1$ to
$\sim4\,\textrm{kpc}$, related to the gas inflow in this region. {\color{red}
I will add the actual points from ref.\cite{2012ARAA..50..531K} (Fig. 7), but
just placing approx horizontal lines for now. The profiles are roughly flat
anyways.}}
\label{fig:surf}
\end{figure}

@@

\begin{figure}[t!]%
\centering
\includegraphics[width=0.45\textwidth]{fig/fig-A2.pdf}
\caption{The time evolution of the bar strength, measured as the second
Fourier component divided by the zeroth Fourier component (a formula is given
in the Methods section). We see that in the \Nbody{} case (blue) the bar
strength increases with time, consistent with previous results showing that
the bar strength increases as bars slow down. In the SMUGGLE case (orange), we
see that the bar strength remains roughly constant, possibly slightly
decreasing with time. This is also consistent with the expected relation
between pattern speed and strength since the bar in this case is not slowing
down.}
\label{fig:strength}
\end{figure}

\begin{figure*}[t!]%
\centering
\includegraphics[width=0.95\textwidth]{fig/fig-bar_decomp.pdf}
\caption{Demonstration of our bar decomposition procedure based on
ref.\cite{2016MNRAS.463.1952P} The \textit{left panel} shows a surface density
projection through the stellar component of the \Nbody{} simulation (disk and
bulge). The \textit{middle panel} shows the component of the disk identified
as being trapped in the bar while the \textit{right panel} shows the component
of the disk identified as not being trapped in the bar. The fact that the
untrapped stars form a roughly axisymmetric structure indicates our bar
decomposition is sufficiently accurate. {\color{red} I will remake this figure
- I ended up losing the files which stored the bar membership, so I just
pulled these screenshots from an earlier presentation.}}
\label{fig:decomp}
\end{figure*}

>>>>

\begin{figure*}[h!]%
\centering
\includegraphics[width=18cm]{fig/fig1.pdf}
\caption{Surface density projections in an \Nbody{} only simulation (upper
panels) and a simulation which includes the SMUGGLE model (bottom panels). We
can see that in the \Nbody{} run, the bar grows in length and strength. In the
SMUGGLE run (which includes a gaseous phase and a model for the multi-phase
interstellar medium), the bar remains at approximately the same length and
strength over the course of the simulation. The \Nbody{} model is identical to
the GALAKOS model, discussed in the text.}\label{fig:overview}
\end{figure*}

\begin{figure}[h!]%
\centering
\includegraphics[width=9cm]{fig/fig2.pdf}
\caption{Various bar properties from the \Nbody{} and SMUGGLE runs. The
\textit{upper panel} show the evolution of the pattern speed. As expected, the
bar in the \Nbody{} run slows down due to interactions between the bar and the
dark matter halo. However, the bar in the SMUGGLE run does not slow down and
instead remains at a constant pattern speed. The \textit{middle panel} shows
the evolution of the bar length. In the \Nbody{} case, the bar lengthens. This
occurs because as the pattern speed drops, bar-like orbits at larger radii are
possible. Stars are captured on these orbits, lengthening the bar. This
process does not occur in the SMUGGLE cases since the bar pattern speed is not
decreasing, and therefore the bar length remains constant. The \textit{lower
panel} shows the torque on the bar by different components. The solid lines
show the torque exerted by the halo in both the \Nbody{} and SMUGGLE cases. The
dashed line shows the torque exerted by the gas phase in the SMUGGLE run
(there is no gas in the \Nbody{} run). Details on how these properties
are calculated is given in the Methods section.}\label{fig:prop}
\end{figure}

\begin{figure*}[h!]%
\centering
\includegraphics[width=18cm]{fig/fig3.pdf}
\caption{The wake excited in the dark matter halo in the \Nbody{} case
(\textit{left panel}) and SMUGGLE case (\textit{right panel}) after
$2.6\,\textrm{Gyr}$. The \textit{left} and \textit{right panels} show a
surface density projection in the $x$-$y$ plane of the dark matter halo after
an axisymmetric average has been subracted. The solid line indicates the
direction of the bar while the dashed line indicates the direction of the halo
wake (both measured by taking the second Fourier component within a sphere of
all material within a radius of $X\,\textrm{kpc}$). The \textit{center panel}
shows the time evolution of the angle difference between the bar and the halo
wake, as measured from the second Fourier component. After the first Gyr, the
angle difference in the SMUGGLE case is smaller than in the \Nbody{} case by
about a factor of two, reflecting how the dark matter halo in the SMUGGLE case
is unable to exert as negative a torque on the bar as in the \Nbody{}
case.}\label{fig:wake}
\end{figure*}

\begin{figure}[h!]
\centering
\includegraphics[width=9cm]{fig/fig4.pdf}
\caption{The torque on the bar by the gas when the pattern speed of the bar is
kept at a constant value. Only gas within the corotation radius is able to
infall. Since slower bars have larger corotation radii, slower bars experience
a larger net torque than faster bars. The setup of the simulations used here
is identical to the SMUGGLE case discussed earlier and in the Methods section,
except the \Nbody{} disk is rotated as a solid body with a constant angular
velocity.}\label{fig:equil}
\end{figure}

@@

\begin{figure}[t]%
\centering
\includegraphics[width=9cm]{fig/fig-vcirc.pdf}
\caption{The circular velocity curve for the \Nbody{} run (blue) and the SMUGGLE
run (orange) compared to observational estimates for the Milky
Way.\cite{2019ApJ...871..120E} We see that the circular velocity curve for
both runs is marginally larger than the Milky Way's, but still comparable. The
SMUGGLE circular velocity curve is larger than the \Nbody{} curve due to the
additional mass in the gas phase.}
\label{fig:vcirc}
\end{figure}

@@

\begin{figure}[t!]%
\centering
\includegraphics[width=9cm]{fig/fig-surf.pdf}
\caption{The time evolution of the gas surface density (\textit{upper}) and
the star formation rate (SFR) surface density (\textit{lower}) at various
times during the simulation. Colored lines indicate the profiles at selected
times during the simulation while the horizontal dashed lines indicate
approximate values for the Milky Way.\cite{2012ARAA..50..531K} We see that the
gas surface density is slightly higher but within an order of magnitude of the
Milky Way's typical gas surface density. We see a sharp decrease in the gas
and SFR surface density along the extent of the bar from $\sim1$ to
$\sim4\,\textrm{kpc}$, related to the gas inflow in this region. {\color{red}
I will add the actual points from ref.\cite{2012ARAA..50..531K} (Fig. 7), but
just placing approx horizontal lines for now. The profiles are roughly flat
anyways.}}
\label{fig:surf}
\end{figure}

@@

\begin{figure}[t!]%
\centering
\includegraphics[width=9cm]{fig/fig-A2.pdf}
\caption{The time evolution of the bar strength, measured as the maximum of the second
Fourier component divided by the zeroth Fourier component (a formula is given
in the Methods section). We see that in the \Nbody{} case (blue) the bar
strength increases with time, consistent with previous results showing that
the bar strength increases as bars slow down. In the SMUGGLE case (orange), we
see that the bar strength remains roughly constant, possibly slightly
decreasing with time. This is also consistent with the expected relation
between pattern speed and strength since the bar in this case is not slowing
down.}
\label{fig:strength}
\end{figure}

\begin{figure*}[t!]%
\centering
\includegraphics[width=18cm]{fig/fig-bar_decomp.pdf}
\caption{Demonstration of our bar decomposition procedure based on
ref.\cite{2016MNRAS.463.1952P} The \textit{left panel} shows a surface density
projection through the stellar component of the \Nbody{} simulation (disk and
bulge). The \textit{middle panel} shows the component of the disk identified
as being trapped in the bar while the \textit{right panel} shows the component
of the disk identified as not being trapped in the bar. The fact that the
untrapped stars form a roughly axisymmetric structure indicates our bar
decomposition is sufficiently accurate. {\color{red} I will remake this figure
- I ended up losing the files which stored the bar membership, so I just
pulled these screenshots from an earlier presentation.}}
\label{fig:decomp}
\end{figure*}
